---
title: "test"
author: "Xinyi Lin"
date: "9/18/2018"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to present a couple of basic plots using `ggplot`.

First we create a dataframe containing variables for our plots.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell